Joshua 2.0: A Toolkit for Parsing-Based Machine Translation \\with Syntax, Semirings, Discriminative Training and Other Goodies

### 2010-04-23 papers/wmt10/joshua-progress.tex
More syntax edits.
git-svn-id: https://joshua.svn.sourceforge.net/svnroot/joshua/branches/publications@1641 0ae5e6b2-d358-4f09-a895-f82f13dd62a4

\section{Support for Syntax-Augmented MT}
The syntax-augmented approach to hierachical phrase-based machine
translation introduced by \newcite{samt2006} aims at improving
translation quality by introducing syntactic information into the
decoding process. To this end, one side of the bitext is parsed and a
syntax-augmented grammar containing additional nonterminal symbols is
extracted. These new symbols are obtained by annotating the
nonterminals in Hiero-style rules
\begin{center}
\begin{tabular}{c}
  {\small \tt [X]} $\Rightarrow$ {\small \tt [X,1]} sans {\small \tt [X,2]} 
  $\vert$ {\tt \small [X,1]} without {\small \tt [X,2]}
\end{tabular}
\end{center}
extracted from the bitext, the nonterminals are labeled according to
which constituents cover the nonterminal span on the parsed side of
the bitext.
\begin{center}
\begin{tabular}{c}
  {\small \tt [VP]} $\Rightarrow$ {\small \tt [VBN,1]} sans {\small
    \tt [NP,2]} $\vert$ $\mathit{VBN}_1$ without {\small \tt [NP,2]} \\
  {\small \tt [NP]} $\Rightarrow$ {\small \tt [NP,1]} sans {\small
    \tt [NP,2]} 
  $\vert$ {\small \tt [NP,1]} without {\small \tt [NP,2]} 
\end{tabular}
\end{center}
To ensure good coverage, the SAMT approach concatenates syntactic
constituents or uses CCG-style labels when there is no single
constituent spanning a nonterminal. The resulting grammar

\joshua's decoder supports SAMT-style grammars as well as non-syntactic
nonterminal annotations. An SAMT grammar

>>>>

\section{Support for Syntax-Augmented MT}
The syntax-augmented approach to hierachical phrase-based machine
translation introduced by \newcite{samt2006} aims at improving
translation quality by introducing syntactic information into the
decoding process. To this end, one side of the bitext is parsed and a
syntax-augmented grammar containing additional nonterminal symbols is
extracted. These new symbols are obtained by annotating the
nonterminals in Hiero-style rules
\begin{center}
\begin{tabular}{c}
  {\small \tt [X]} $\Rightarrow$ {\small \tt [X,1]} sans {\small \tt [X,2]} 
  $\vert$ {\tt \small [X,1]} without {\small \tt [X,2]}
\end{tabular}
\end{center}
extracted from the bitext, the nonterminals are labeled according to
which constituents cover the nonterminal span on the parsed side of
the bitext.
\begin{center}
\begin{tabular}{c}
  {\small \tt [VP]} $\Rightarrow$ {\small \tt [VBN,1]} sans {\small
    \tt [NP,2]} $\vert$ $\mathit{VBN}_1$ without {\small \tt [NP,2]} \\
  {\small \tt [NP]} $\Rightarrow$ {\small \tt [NP,1]} sans {\small
    \tt [NP,2]} 
  $\vert$ {\small \tt [NP,1]} without {\small \tt [NP,2]} 
\end{tabular}
\end{center}
To ensure good coverage, the SAMT approach concatenates syntactic
constituents or uses CCG-style labels when there is no single
constituent spanning a nonterminal. The derivations licensed by the
resulting grammar are constrained to match the syntactic structure,
typically leading to more consistent reorderings.

\joshua's decoder supports SAMT-style grammars as well as non-syntactic
nonterminal annotations obtained from other sources, such as named
entity taggers.
